Constructing Sailing Match Race Schedules: Round Robin Pairing Lists

### 2015-03-24 paper.tex
Change GCC phrasing

\newcommand{\globalCardinality}{\mathrm{globalCardinality}}
\newcommand{\allDifferent}{\mathrm{allDifferent}}

@@

\begin{flalign}
& f = \lceil n(n-1)/m  \rceil \label{eq1} \\
& t = n(n-1)/2 \label{eq2} \\
& \forall_{\tau \in [0..t-1]} ~ \timeSlot[{\tau}] \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
& \forall_{i \in [0..f-1]} ~ \state[{i}] \in \{FIRST,MID,LAST,BYE,END\} \label{eq4} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = FIRST \iff \timeSlot[{i \cdot m}] \geq 0  \label{eq5} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = MID \iff  \exists_{j \in [i.m+1 ..  i.m+m-2]} ~ \timeSlot[{j}] \geq 0  \label{eq6} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = LAST \iff \timeSlot[{(i+1).m - 1}] \geq 0  \label{eq7} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = BYE \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -1  \label{eq8} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -2  \label{eq9} \\
& \globalCardinality(\timeSlot,\{0,..,n-1\} \setminus \{\sigma\},\{1..1\},\{1 .. 1\})
\end{flalign}

@@

A global cardinality constraint \cite{globCard} is then imposed on the array
$\timeSlot$ to ensure that this skipper ($\sigma$)  is in a match with all
other skippers (i.e. $\{0 \ldots n-1 \} \setminus \{\sigma\}$) once (i.e. $\{1 \ldots
1\}$) and once only (i.e. $\{1 \ldots 1\}$). The $\state$ variables are then used
to impose match race criteria 4 (if last in flight $i$ then not first in flight
$i+1$), criteria 11 (if last in flight $i$ then not in a bye in flight $i+1$)
and criteria 12 (if flight $i$ is a bye then flight $i$ is not first). In
addition, we have the rule that if a skipper has finished his matches in flight
$i$ (i.e. END) then he has finished his matches in flight $i+1$ (and so on).
These criteria are imposed on the $\state$ variables via a deterministic finite
automata (DFA) constraint \cite{Pesant04}.

>>>>

\newcommand{\eachOccursExactlyOnce}{\mathrm{eachOccursExactlyOnce}}
\newcommand{\allDifferent}{\mathrm{allDifferent}}

@@

\begin{flalign}
& f = \lceil n(n-1)/m  \rceil \label{eq1} \\
& t = n(n-1)/2 \label{eq2} \\
& \forall_{\tau \in [0..t-1]} ~ \timeSlot[{\tau}] \in \{-2..t-1\} \setminus \{\sigma\} \label{eq3} \\
& \forall_{i \in [0..f-1]} ~ \state[{i}] \in \{FIRST,MID,LAST,BYE,END\} \label{eq4} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = FIRST \iff \timeSlot[{i \cdot m}] \geq 0  \label{eq5} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = MID \iff  \exists_{j \in [i.m+1 ..  i.m+m-2]} ~ \timeSlot[{j}] \geq 0  \label{eq6} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = LAST \iff \timeSlot[{(i+1).m - 1}] \geq 0  \label{eq7} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = BYE \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -1  \label{eq8} \\
& \forall_{i \in [0..f]} ~ \state[{i}] = END \iff  \forall_{j \in [i.m ..  m.(i+1)-1]} ~ \timeSlot[j] = -2  \label{eq9} \\
& \eachOccursExactlyOnce(\timeSlot, \{0, \ldots, n-1\} \setminus \{\sigma\}\})
\end{flalign}

@@

We must then ensure that each skipper $\sigma$ is in a match with all other
skippers $\{0, \ldots, n-1\} \setminus \{sigma\}$. This may be done by imposing
a global cardinality constraint \cite{globCard} on the array $\timeSlot$. The
$\state$ variables are then used to impose match race criteria 4 (if last in
flight $i$ then not first in flight $i+1$), criteria 11 (if last in flight $i$
then not in a bye in flight $i+1$) and criteria 12 (if flight $i$ is a bye then
flight $i$ is not first). In addition, we have the rule that if a skipper has
finished his matches in flight $i$ (i.e. END) then he has finished his matches
in flight $i+1$ (and so on).  These criteria are imposed on the $\state$
variables via a deterministic finite automata (DFA) constraint \cite{Pesant04}.
